%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% One Page Two Column Resume
% LaTeX Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Arindam}{Pradhan}{ \urlstyle{same}\url{http://arindampradhan.github.io/} \\
\href{mailto:arindamrpadhan10@gmail.com}{arindampradhan10@gmail.com} | (+91) 9078954415
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{C.E.T}
\descript{B.Tech in Electrical Engineering}
\location{Expected AUG 2016 | BBSR, IND \\
Major CGPA: 7.64 / 10 }
\sectionsep


%\descript{BS in Computer Science}
%\location{Expected May 2014 | Ithaca, NY}
%Conc. in Software Engineering \\
%College of Engineering \\
%Dean's List (All Semesters) \\
%\location{ Cum. GPA: 3.92 / 4.0 \\
%Major GPA: 3.94 / 4.0}
%\sectionsep

%\subsection{La Martiniere for Boys}
%\location{Grad. May 2011|  Kolkata, India}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/arindampradhan}{\custombold{arindampradhan}} \\
LinkedIn://  \href{https://in.linkedin.com/in/arindampradhan}{\custombold{arindampradhan}} \\
%YouTube://  \href{https://www.youtube.com/user/DeedyDash007}{\custombold{DeedyDash007}} \\
Twitter://  \href{https://twitter.com/rrindam}{\custombold{@rrindam}} \\
Quora://  \href{https://www.quora.com/profile/Arindam-Pradhan}{\custombold{Arindam-Pradhan}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
%\subsection{Graduate}
%Advanced Machine Learning \\
%Open Source Software Engineering \\
%Advanced Interactive Graphics \\
%Compilers + Practicum \\
%Cloud Computing \\
%\sectionsep

\subsection{Undergraduate}
DataStructure \\
C, C++ \\
Machine Learning (Coursera) \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Good:}
\textbullet{} Python \textbullet{} javascript/node \break \textbullet{} html/css \\
\location{Average:}
\textbullet{} go \textbullet{} csharp \\
\location{Shell:}
\textbullet{} bash \textbullet{} zsh \\
\location{Familiar Databases}
\textbullet{} MongoDB \textbullet{} Redis \\
\location{OS:}
Linux(comfortable) \textbullet{} Windows \\
\sectionsep

%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Activities}
\location{PyBelgaum | Wrapping a json API}
\textbullet{} Speaker \\
\textbullet{} Gave a talk on my project about how to write api client of a rest api and packaging it. \\
\location{Startup weekend Vishakapatnam}
\textbullet{} Speaker \\
\textbullet{} Helped some startups implement their ideas \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Nowfloats}
\descript{|  Software Developer}
\location{July 2016 – Present }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked on the management dashboard of the company.
\item Implemented Instamojo payment gateway | Indian payment company.
\item Facebook and Twitter signin to fetch access tokens for posting on behalf of users.
\item Bug fixes regarding customer issues.
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\end{tightemize}

\runsubsection{Nowfloats Hackathon}
\descript{|  Product Competitor Visualizer}
\location{November 2016}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Visualize the market compitor of a product in nearyby area and in online presence.
\item Technologies Used: D3.js, Angular, Algolia, nodejs and python.
\item Hosting on an ec2 vm(AWS), serving on Nginx and searh engine used Algolia.
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\end{tightemize}

\runsubsection{Sormen}
\descript{| Startup Company | Intern}
\location{December 2015 – Feb 2016 | Singapore | Remote-work}
\begin{tightemize}
\item \emph{Project goal :} A social network for school students and university courses.
\item \emph Crawled singapore university websites for the courses they are providing. Wrote a django app with google and linkedin signin oauth enabled \end{tightemize}
\sectionsep

\runsubsection{Openhatch}
\descript{| Open Source Contributor | Django Project}
\location{Dec 2014 – April 2015 }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Openhatch is a company that introduces and teaches people about opensource.
\item I fixed bugs regarding authentication, wrote documentation about git and how it is used in large organization with contributors.\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SIDE PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Side Projects}

\runsubsection{pok}
\descript{| Manage your pocket from terminal}
{ \urlstyle{same}\url{http://arindampradhan.github.io/pok/} }\\
%\begin{tightemize}
%\item Chrome extensions only gives saving options.\item So wrote a terminal app with Methods: Add, delete, save, search tag and name.\end{tightemize}
\sectionsep

\runsubsection{Py\_projects}
\descript{| Wrote around 30 python mini projects. }
{ \urlstyle{same}\url{https://github.com/arindampradhan/py_projects/} }\\
\sectionsep

\runsubsection{material-lite-snippet}
\descript{| Material Plugin for sublime}
{ \urlstyle{same}\url{https://github.com/arindampradhan/material-lite-snippet} }\\
\sectionsep

\runsubsection{hey\_shorty}
\descript{| High performance redis based url shortener}
{ \urlstyle{same}\url{https://github.com/arindampradhan/hey_shorty} }\\
\sectionsep

\runsubsection{yaaHN}
\descript{| Python wrapper for firebase hacker news api and write a mock of hacker news using it}
{ \urlstyle{same}\url{https://github.com/arindampradhan/yaaHN/} }\\
%\begin{tightemize}
%\item Python wrapper for firebase hacker news api.
%\item Implementation: mockHN – A django app on top of yaaHN. Mocks the hacker news website with real-time data.\end{tightemize}
\sectionsep

\runsubsection{cheesy}
\descript{| Command line tool for pypi | python}
{ \urlstyle{same}\url{http://arindampradhan.github.io/cheesy/} }\\
\sectionsep

\runsubsection{ProductHunt\_API}
\descript{| Unofficial python API for Product Hunt}
{ \urlstyle{same}\url{https://github.com/arindampradhan/ProductHunt_API/} }\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\end{document}  \documentclass[]{article}
